Codebook
========
 
Descriptions of VAriables
------------------------------
  
  Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity 
activity         | Activity description
featDomain       | Feature: Time/Frecuency domain signal 
featInstrument   | Feature: Measuring Instrument
featAcceleration | Feature: Acceleration Signal
featVariable     | Feature: Variable (Mean or Stand.Dev)
featJerk         | Feature: Jerk Signal
featMagnitude    | Feature: Magnitude of the signals
featAxis         | Feature: 3-axial signals 
featCount        | Feature: Count of data points 
featAverage      | Feature: Average of variables for activity and subject

Structure
-----------
  
  ```{r}
str(dataTidy)
```

key variables
--------------
  
  ```{r}
key(dataTidy)
```

Rows of the dataset
-------------------
  
  ```{r}
dataTidy
```

Summary
-------
  
  ```{r}
summary(dataTidy)
```

Posible Features
----------------
  
  ```{r}
dataTidy[, .N, by=c(names(dataTidy)[grep("^feat", names(dataTidy))])]
```

Save to txt file
------------
  
  Save data table objects to a tab-delimited text file called `TidyDataSet.txt`.

```{r}
val <- file.path(Dir, "TidyDataSet.txt")
write.table(dataTidy, val, quote=FALSE, sep="\t", row.names=FALSE)
