---
title: "Peer Evaluation Project-getdata-008"
author: "Erik Rodriguez Pacheco"
date: "Wednesday, October 22, 2014"
output: html_document
---

## Initial preparation


Load the packages and set working directory

```{r}
library(data.table)
library(reshape2)
library(knitr)
library(markdown)
Dir <- getwd()
Dir
```

## Obtaining the data
  
Download data in Assingment folder

```{r, eval=FALSE}
link <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
x <- "Data.zip"
if (!file.exists(Dir)) {dir.create(Dir)}
download.file(link, file.path(Dir, x))
```

## Extract Data for working

Running external program 7zip to extract data from zip dowloaded

```{r}
zip <- file.path("C:", "Program Files", "7-Zip", "7z.exe")
set<-"x"
extract <- paste(paste0("\"", zip, "\""), set, paste0("\"", file.path(Dir, x), "\""))
suppressMessages(suppressWarnings(system(extract)))
```

The file contains the directory UCI HAR Dataset will be the new directory
This is a list of the files inside that directory

```{r}
Dirdata <- file.path(Dir, "UCI HAR Dataset")
list.files(Dirdata, recursive=TRUE)

```

## Read Information with data.table and read table


Is necesary read data from Subject Files and the activity train
```{r}
SubjTrain <- fread(file.path(Dirdata, "train", "subject_train.txt"))
SubjTest  <- fread(file.path(Dirdata, "test" , "subject_test.txt" ))
```

```{r}
ActTrain <- fread(file.path(Dirdata, "train", "Y_train.txt"))
ActTest  <- fread(file.path(Dirdata, "test" , "Y_test.txt" ))
```



Now is necesary read the data 

fread function is not working very well for import data from X_train,txt and X.test.txt.
alternative solution is use read table, create data frame and finally transform this data frame 
in data.table objects

```{r}
#Train <- fread(file.path(Dirdata, "train", "X_train.txt"))
#Test  <- fread(file.path(Dirdata, "test" , "X_test.txt" ))
Train<-read.table(file.path(Dirdata, "train", "X_train.txt"))
Test<-read.table(file.path(Dirdata, "test", "X_test.txt"))
Train<-data.table(Train)
class(Train)
Test<-data.table(Test)
class(Test)
```


## 1-Merges the training and the test sets to create one data set
  
```{r}
Subject <- rbind(SubjTrain, SubjTest)
setnames(Subject, "V1", "subject")
Activity <- rbind(ActTrain, ActTest)
setnames(Activity, "V1", "activityNum")
data <- rbind(Train, Test)

Subject <- cbind(Subject, Activity)
data <- cbind(Subject, data)

setkey(data, subject, activityNum)
```

## 2-Extracts only the measurements on the mean and standard deviation for each measurement

```{r}
Feat <- fread(file.path(Dirdata, "features.txt"))
setnames(Feat, names(Feat), c("featureNum", "featureName"))
Feat <- Feat[grepl("mean\\(\\)|std\\(\\)", featureName)]
Feat$featureCode <- Feat[, paste0("V", featureNum)]
head(Feat)
Feat$featureCode
subset <- c(key(data), Feat$featureCode)
data <- data[, subset, with=FALSE]
head(data)
```

## 3-Uses descriptive activity names to name the activities in the data set

```{r}
ActNames <- fread(file.path(Dirdata, "activity_labels.txt"))
setnames(ActNames, names(ActNames), c("activityNum", "activityName"))

```

## 4-Appropriately labels the data set with descriptive activity names.

```{r}

data <- merge(data, ActNames, by="activityNum", all.x=TRUE)
setkey(data, subject, activityNum, activityName)

data <- data.table(melt(data, key(data), variable.name="featureCode"))
data <- merge(data, Feat[, list(featureNum, featureCode, featureName)], by="featureCode", all.x=TRUE)
data$activity <- factor(data$activityName)
data$feature <- factor(data$featureName)
```

Seperate features from FeatureName

```{r SepFeatures}
SepFeatures <- function (regex) {
  grepl(regex, data$feature)
}

n <- 2
y <- matrix(seq(1, n), nrow=n)
x <- matrix(c(SepFeatures("^t"), SepFeatures("^f")), ncol=nrow(y))
data$featDomain <- factor(x %*% y, labels=c("Time", "Freq"))
x <- matrix(c(SepFeatures("Acc"), SepFeatures("Gyro")), ncol=nrow(y))
data$featInstrument <- factor(x %*% y, labels=c("Accelerometer", "Gyroscope"))
x <- matrix(c(SepFeatures("BodyAcc"), SepFeatures("GravityAcc")), ncol=nrow(y))
data$featAcceleration <- factor(x %*% y, labels=c(NA, "Body", "Gravity"))
x <- matrix(c(SepFeatures("mean()"), SepFeatures("std()")), ncol=nrow(y))
data$featVariable <- factor(x %*% y, labels=c("Mean", "SD"))
data$featJerk <- factor(SepFeatures("Jerk"), labels=c(NA, "Jerk"))
data$featMagnitude <- factor(SepFeatures("Mag"), labels=c(NA, "Magnitude"))

n <- 3
y <- matrix(seq(1, n), nrow=n)
x <- matrix(c(SepFeatures("-X"), SepFeatures("-Y"), SepFeatures("-Z")), ncol=nrow(y))
data$featAxis <- factor(x %*% y, labels=c(NA, "X", "Y", "Z"))
```

```{r}
x1 <- nrow(data[, .N, by=c("feature")])
x2 <- nrow(data[, .N, by=c("featDomain", "featAcceleration", "featInstrument", "featJerk", "featMagnitude", "featVariable", "featAxis")])
identical(x1,x2)
```


## 5-Creates a second, independent tidy data set with the average of each variable for 
## each activity and each subject.


```{r}
setkey(data, subject, activity, featDomain, featAcceleration, featInstrument, featJerk, featMagnitude, featVariable, featAxis)
dataTidy <- data[, list(count = .N, average = mean(value)), by=key(data)]
dataTidy
```

## Codebook

```{r}
knit("makeCodebook.Rmd", output="Codebook.md", encoding="ISO8859-1")
markdownToHTML("Codebook.md", "Codebook.html")
```
